Foregrounds in Fourier Delay Space for Wide--Field Redshifted 21~cm Observatories

### 2015-02-09 ms.tex
Create subsection for Fourier delay space
from edcebe0:
============

In ms.tex,

(*) Create new subsection Fourier delay space under Delay Spectrum
section
(*) Reshuffle a paragraph within th Delay Spectrum section
(*) Change wording in Delay Spectrum section slightly
(*) Change wording in subsection Delay Spectrum Deconvolution

@@

The spectral transfer function of the instrument convolves the {\it foreground wedge} and stretches it further (unshaded narrow strips bounded by solid and dashed lines) along $\tau$--axis \citep{par12b,thy13}. The width of this narrow strip is inversely proportional to the operating bandwidth. The region of Fourier space excluding the {\it foreground wedge} and the narrow strips is the so--called {\it EoR window}, shown in light and medium shades. {\bf In the context of EoR studies in Fourier space, the H{\sc i} power spectrum from the EoR is expected to decrease rapidly with $|\boldsymbol{k}|$. Hence, the brightest EoR signal will be observed on the shortest baselines and smallest delays. Thus the region of interest for EoR studies relying on {\it avoidance} strategy is just beyond the horizon delay limits (dashed lines) on short baselines, marked as the region of {\it maximal EoR sensitivity}}.

@@

In our present study, we use a latitude of -26.701\arcdeg and an antenna layout identical to that of the MWA \citep{bea12}. The array is arranged as a centrally condensed core of $\sim$~300~m --- there are many spacings in the range 5--50~m --- and a radial density that falls off as the inverse of the radius, with the longest baselines at 3~km. Here we focus on antenna spacings $|\boldsymbol{b}| \le 200$~m (spatial scales relevant to reionization). {\bf Their deviation from coplanarity is negligible}. For geometrical intuition, we restrict the orientation ($\theta_b$, measured anti-clockwise from East) of all baselines to lie in the range $-67.5\arcdeg \leq \theta_b < 112.5\arcdeg$. Baselines oriented in the other half--plane measure conjugate visibilities with delays of equal magnitude but of opposite sign and hence are ignored in our analysis. {\bf Note that visibilities from different baselines have not been averaged together in this analysis}.

@@

We obtain the delay spectrum of visibilities by taking the delay transform of each baseline's spectrum (equation~\ref{eqn:delay-transform}) choosing $W'_f$ to be a {\it Blackman--Harris} window function. The sky spectrum is multiplied by weights, $W_f$, due to the instrumental passband and channels possibly flagged for interference. In delay--space, these weights translate into a convolution by a point spread function (PSF). We deconvolve this PSF using a one dimensional CLEAN algorithm \citep{tay99} as described for the delay axis \citep{par09,par12b} to obtain the final delay spectra. The CLEAN procedure iteratively finds and subtracts peak values convolved by the Fourier transform of the weights. We limit the selection of peaks to modes inside the horizon delay limit, corresponding to smooth spectrum objects in the visible sky hemisphere.

>>>>

In our present study, we use a latitude of -26.701\arcdeg~ and an antenna layout identical to that of the MWA \citep{bea12} for the observatory. The array is arranged as a centrally condensed core of $\sim$~300~m --- there are many spacings in the range 5--50~m --- and a radial density that falls off as the inverse of the radius, with the longest baselines at 3~km. Here we focus on antenna spacings $|\boldsymbol{b}| \le 200$~m (spatial scales relevant to reionization). {\bf Their deviation from coplanarity is negligible}. For geometrical intuition, we restrict the orientation ($\theta_b$, measured anti-clockwise from East) of all baselines to lie in the range $-67.5\arcdeg \leq \theta_b < 112.5\arcdeg$. Baselines oriented in the other half--plane measure conjugate visibilities with delays of equal magnitude but of opposite sign and hence are ignored in our analysis. {\bf Note that visibilities from different baselines have not been averaged together in this analysis}.

\subsection{Fourier Delay Space}\label{sec:delay-space}

@@

The spectral transfer function of the instrument convolves the {\it foreground wedge} and stretches it further (unshaded narrow strips bounded by solid and dashed lines) along $\tau$--axis \citep{par12b,thy13}. The width of this narrow strip is inversely proportional to the operating bandwidth. The region of Fourier space excluding the {\it foreground wedge} and the narrow strips is the so--called {\it EoR window}, shown in light and medium shades. {\bf In the context of EoR studies in Fourier space, the H{\sc i} power spectrum from the EoR is expected to decrease rapidly with $|\boldsymbol{k}|$. Hence, the brightest EoR signal will be observed on the shortest baselines and smallest delays. Thus the regions of interest for EoR studies relying on {\it avoidance} strategy are just beyond the horizon delay limits (dashed lines) on short baselines, marked as regions of {\it maximal EoR sensitivity}}.

@@

@@

We obtain the delay spectrum of visibilities by taking the delay transform of each baseline's spectrum (equation~\ref{eqn:delay-transform}) choosing $W'_f$ to be a {\it Blackman--Harris} window function. The sky spectrum is multiplied by weights, $W_f$, due to the instrumental passband and frequency channels possibly flagged for radio frequency interference. In delay--space, these weights translate into a convolution by a point spread function (PSF). We deconvolve this PSF using a one dimensional CLEAN algorithm \citep{tay99} as described for the delay axis \citep{par09,par12b} to obtain the final delay spectra. The CLEAN procedure iteratively finds and subtracts peak values convolved by the Fourier transform of the weights. We limit the selection of peaks to modes inside the horizon delay limit, corresponding to smooth spectrum objects in the visible sky hemisphere.
